Estimating Gaze Duration Error Distributions from Eye Tracking Data

### 2022-05-04 paper/paper.tex
Paper update

Eye tracking applications produce a series of gaze fixation points that can be attributed to
objects within a subjects field of vision. Error is typically measured on the basis of individual
gaze fixation measurements. However, often these applications are used to infer a gaze duration
metric from a series of fixation measurements. In this work we deliver an open source application
that estimates the error distribution of gaze duration estimates from an eye tracking validation
log file.

@@

Eye tracking applications are an important technology that permit the development of a wide 
variety of new forms of software interaction, as well as a tool for empirical investigations 
into human thought and behaviour. Eye tracking studies are widely used as a method of 
measuring overt attention to visual stimuli and have been applied to study the extent to 
which people look at, and remember, advertising \cite{Hervet2011}.
The technology has also allowed the study of many factors that contribute to effective advertising,
including the impact of images of faces \cite{Djamasbi2010},
the use of animation \cite{Hamborg2012} and the relationship with
social media posts \cite{Barreto2013}.

@@

Gaze fixation models will typically have an error profile that is dependent on both 
the nature of the media being presented, the variety of faces and lighting conditions 
in the training data. In addition, it has been observed that the error profile varies 
depending on the location of the true fixation point.

@@

We apply this grid of error probabilities in a Monte Carlo simulation that requires the following inputs:
1.	The grid coordinates in which the item of concern is located.
2.	The duration of true fixation on that item
3.	The duration of the entire session of measurement.
The Monte Carlo process will then repeatedly simulate sessions of the given length and gaze duration. Each simulation will use the error profiles to produce a potential model output. Collectively these estimates model outputs constitute a probability distribution over outputs for the given scenario.

@@

@@

@@

>>>>

Eye tracking applications produce a series of gaze fixation points that can be attributed to
objects within a subject's field of vision. Error is typically measured on the basis of individual
gaze fixation point measurements. However, often these applications are used to infer a gaze duration
metric from a series of fixation measurements. In this work we develop an algorithm for estimating
the error bounds on gaze duration measurement through monte carlo simualtion based on the content
of an eye tracking validation log file. We provide this algorithm as an open source application
that allows for robust estimates of the error distribution of gaze duration measurements. 
We use this application to conduct experiments on the expected error bounds for different duration
measurements across a range of session lengths and area of interest positions within the viewport
of mobile devices. The results indicate...

@@

Eye tracking is an important technology with a wide variety of applications. It permits evaluation
of software user interfaces\cite{Harezlak2015}, the development of new forms of software interaction, as well as a potential method of biometric identification\cite{Kasprowski2018}. 
Eye tracking has become a core tool for empirical investigations 
into human behaviour and is widely used as a method of measuring explicit attention to visual stimuli. 
It has been applied to study psychological phenomena ranging from cognition\cite{Brunye2019}
to mental health\cite{Duque2014,Rudich-Strassler2022}, and is now routinely used to evaluate 
advertising \cite{Hervet2011}. Eye tracking technology has allowed the marketing researchers 
to study many factors that contribute to effective advertising, 
including brand recall \cite{Wedel2000},
the capture and tranfer of attention \cite{Pieters2004}, 
the impact of images of faces \cite{Djamasbi2010},
the attention effects of animation \cite{Hamborg2012},
and the relationship with social media posts \cite{Barreto2013}.

@@

Gaze fixation models will typically have an error profile that is dependent on both 
the nature of the media being presented, the variety of faces and lighting conditions 
in the training data. In addition, it has been observed that the error profile varies 
depending on the location of the true fixation point within the subjects field of view.
The errors in fixation point measurement for a given eye tracking solution are routinely
adjusted through a process called calibration. Improvements in the callibration process
are an ongoing focus for the development of algorithms\cite{Zhang2014,Hassoumi2019} 
and software tools\cite{ETCAL2018}

@@

We apply this grid of error probabilities in a Monte Carlo simulation that requires the following inputs:
1.	The grid coordinates in which the item of concern is located.
2.	The duration of true fixation on that item
3.	The duration of the entire session of measurement.

The Monte Carlo process will then repeatedly simulate sessions of the given length and gaze duration. Each simulation will use the error profiles to produce a potential model output. Collectively these estimates model outputs constitute a probability distribution over outputs for the given scenario.

@@

\subsection{Experiments}

We evaluate the methodology by conducting experiments over a range of AOI positions and session
lengths. The goal of which is to understand changes in the expected error profile of 
visual attention measurement when the object position varies and under variations in the
length of time that a subject is tracked.

In both instances we use an identical validation dataset generated from a panel of 15 users
engaged in a validation task after calibration with the SeeSo eye tracking software on mobile
devices. In these experiments we have used all validation data as single source of error 
estimation, but in principle these experiments could be conducted on a per user basis.

@@

We show all experimental results in Figure \ref{fig:plots}. The top series corresponds
to experiments where the AOI is the top third of the viewport, the middle and bottom 
series correspond to their respective thirds of the viewport. In each plot we show
data for a specific session length ranging from 10 to 30 seconds, where the x axis
depicts the measured gaze duration and the y-axis shows the confidence range for the
true gaze duration.

@@

Not sure yet.
